PineAPPL: EW and mixed QCD--EW corrections for PDF fits

### 2020-07-30 paper/sec-results.tex
Nine point scale variation

The central values of the renormalisation and factorisation scales, $\mu_R$ and
$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
of the $Z$-boson, for the ATLAS measurement, and the scale
$\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
invariant mass bin, for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of $Z$-boson production with non-zero transverse momentum, we use
$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. As is customary, the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
from the seven-point scale variations is constructed.

>>>>

The central values of the renormalisation and factorisation scales, $\mu_R$ and
$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
of the $Z$-boson, for the ATLAS measurement, and the scale
$\mu_R=\mu_F=M_{\ell\bar\ell}$, where $M_{\ell\bar\ell}$ is the central value of each
invariant mass bin, for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of $Z$-boson production with non-zero transverse momentum, we use
$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. As is customary, the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
from the nine-point scale variations is constructed.
